Notation proposal

### 2011-06-02 notation.tex
more words
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@794 ccdd05d5-56c1-461a-bf98-85f6876523b4
thoughts
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@830 ccdd05d5-56c1-461a-bf98-85f6876523b4

@@

Definition of matched filter:
\begin{equation}
\rho_i [k] = \sum_{n=0}^{N-1} h_{i}[n] x [k-n]
\end{equation}
where $h_i[k]$ denotes the $k^{\mathrm{th}}$ sample of the $i^{\mathrm{th}}$
template waveform and $x[k-n]$ represents the $(k-n)^{\mathrm{th}}$ sample of
the data.

Definition of time slices:
\begin{align}
h_{i}[k] &= \sum_s h_{i}^{s}[k] \\
h_{i}^{s}[k] &= \left\{ \begin{aligned}
    h_{i}[k] & \; \text{if } t^{s+1} < \frac{k}{f} \leq t^{s} \\
    0 & \; \text{, otherwise }
    \end{aligned} \right. \\
h_{i}^{s}[k^{s}] &\equiv h_{i}^{s}\!\left[k\frac{f}{f^{s}}\right]
\end{align}

Throughout, we will use the convention that $k$ indexes time-series sampled at
the full sample rate $f$ and $k^s$ indexes time-series sampled at a reduced
sample rate $f^s$.  For the case of band limited functions it is sufficient to
simply remove sample points to define the downsampled version as is shown in
the previous equation.

Definition of decimation for a function $f$:
\begin{equation}
f[k^{s+1}] = \sum_{n=-N^\shortdownarrow/2}^{N^\shortdownarrow/2-1} b^\shortdownarrow[n] f\!\left[k^{s} - n\right]
\end{equation}

Definition of interpolation for a function $f$:
\begin{equation}
f[k^{s}] = \sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] f\!\left[k^{s+1} - n\right]
\end{equation}

\textsc{svd}:
\begin{equation}
h^{s}_{i}\!\left[k^{s}\right] = \sum_{m=0}^{M-1} v^{s}_{im} \sigma^{s}_m u^{s}_{m}[k^{s}] \approx \sum_{l=0}^{L^s-1} v^{s}_{il} \sigma^{s}_l u^{s}_{l}[k^{s}]
\end{equation}

Early-warning \textsc{snr}:
\newcommand{\mystrut}{\rule[-2em]{0pt}{0pt}}  % line up the underbraces
\begin{equation}
    \rho^{s}_i[k^{s}] = \underbrace{\mystrut\sum_{l=0}^{L^{s}-1} v^{s}_{il} \sigma^{s}_l}_{\substack{\text{Reconstruction}\\ \text{with {\sc SVD}}}}
    \underbrace{\mystrut\sum_{n=0}^{N^{s} - 1} u^{s}_{l}[n] x[k^{s}-n]}_{\substack{\text{orthogonal}\\ \text{{\sc FIR} filter}}} + 
    % + 
    % \underbrace{\mystrut\sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] \sum_{q \in \mathbb{Z}} \delta\!\left[k-n, q \frac{f^{s}}{f^{s+1}}\right]}_\text{interpolation filter} 
    \underbrace{\mystrut\rho^{s+1}_i[k^{s}]}_{\substack{\text{accum.}\\ \text{prior {\sc snr}}}}
\end{equation}

>>>>

\newcommand{\downsample}[1]{\ensuremath{\, \downarrow^{s-1} \star \,\, #1}}
\newcommand{\upsample}[1]{\ensuremath{\, \uparrow^{s+1} \star \,\, #1}}

@@

We define a general discrete time series $p[k]$ with k indicating the time
samples at the maximum sample rate of the analysis.  We define a time series
$p^{s}[k^{s}]$ as being the time series $p[k]$ at a different (and lower)
sample rate $s$.  It is also necessary to thus define the operation that
changes the sample rate.

Decimation:
\begin{equation}
p^{s-1}[k^{s-1}] = \downsample{p^{s}[k^{s}]}
\end{equation}

Interpolation:
\begin{equation}
p^{s+1}[k^{s+1}] = \upsample{p^{s}[k^{s}]}
\end{equation}

In general downsampling and upsampling are a convolution of a antialiasing
filter or an interpolation function, respectively.  In the special case of a
band limited function, decimation may simply reduce to taking every nth sample
point, depending on the relative sample rates.

It is also necessary to introduce notation representing the time slices
of a template $\tau$

Definition of time sliced templates:
\begin{align}
h_{i}[k] &= \sum_{\tau} h_{i}^{\tau}[k] \\
h_{i}^{\tau}[k] &= \left\{ \begin{aligned}
    h_{i}[k] & \; \text{if } t^{\tau} < \frac{k}{f} \leq t^{\tau+1} \\
    0 & \; \text{, otherwise }
    \end{aligned} \right.
\end{align}

Since the templates are band limited an antialiasing filter is not required to
downsample, we need only to remove certain sample points as long as the desired
sample rate is at least twice the frequency content of the template in a time

The index $\tau$ when present will be used to denote a quantity that pertains
to a given time slice.

Definition of matched filter at the full sample rate:
\begin{equation}
\rho_i [k] = \sum_{n=0}^{N-1} h_{i}[n] x [k-n]
\end{equation}
where $h_i[k]$ denotes the $k^{\mathrm{th}}$ sample of the $i^{\mathrm{th}}$
template waveform and $x[k-n]$ represents the $(k-n)^{\mathrm{th}}$ sample of
the data.

Quantities involving the SVD are at a given sample rate $s$ and in a time slice
$\tau$

\textsc{svd}:
\begin{equation}
h^{\tau s}_{i}\!\left[k^{s}\right] = \sum_{m=0}^{M-1} v^{\tau s}_{im} \sigma^{\tau s}_m u^{\tau s}_{m}[k^{s}] \approx \sum_{l=0}^{L^s-1} v^{\tau s}_{il} \sigma^{\tau s}_l u^{\tau s}_{l}[k^{s}]
\end{equation}

Early-warning \textsc{snr}:
\newcommand{\mystrut}{\rule[-2em]{0pt}{0pt}}  % line up the underbraces
\begin{equation}
    \rho^{\tau s}_i[k^{s}] = \underbrace{\mystrut\sum_{l=0}^{L^{s}-1} v^{\tau s}_{il} \sigma^{\tau s}_l}_{\substack{\text{Reconstruction}\\ \text{with {\sc SVD}}}}
    \underbrace{\mystrut\sum_{n=0}^{N^{s} - 1} u^{\tau s}_{l}[n] x[k^{s}-n]}_{\substack{\text{orthogonal}\\ \text{{\sc FIR} filter}}} + 
    % + 
    % \underbrace{\mystrut\sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] \sum_{q \in \mathbb{Z}} \delta\!\left[k-n, q \frac{f^{s}}{f^{s+1}}\right]}_\text{interpolation filter} 
    \underbrace{\mystrut\rho^{\tau - 1 s}_i[k^{s}]}_{\substack{\text{accum.}\\ \text{prior {\sc snr}}}}
\end{equation}
